Performance benefits of Intel Optane DC storage for the parallel processing of large neuroimaging data

### 2019-10-23 paper.tex
fixed discussion

With nearly a four-fold increase in parallelization, the makespan generally did
not improve other but a few 100s on Isilon. Overall, the general trend is similar
than with 25 cpus. As can be seen in Figure~\ref{fig:20mksp96}, tmpfs is the
fastest storage device. Regardless, Optane remains significantly faster than the
other storage devices (e.g. Isilon). However, emulated disk results appear to 
imply that the speedup difference between Optane and local disk will be smaller.

@@

>>>>

With nearly a four-fold increase in parallelization, the makespan generally did
not improve other but a few 100s on Isilon. Overall, the general trend is similar
than with 25 cpus. As can be seen in Figure~\ref{fig:20mksp96}, Optane in Memory
mode is the fastest storage device. Furthermore, Optane in App Direct mode 
remains significantly faster than the other storage devices (e.g. Isilon).
However, emulated disk results appear to imply that the speedup difference
between Optane in App Direct mode and local disk will be smaller than at 25 cpus.

The vast majority of processing time appears to be spent on writing to the 
respective storage device with the exception of Optane in Memory Mode, which 
spends most of its time incrementing (Figure~\ref{fig:20stackedp96}). App Direct
mode executions appear to have reduced incrementation time coupled with increased
write times when compared to their memory mode equivalents. Furthermore, read
times appear to be increased for Isilon memory mode executions. These events are
not reflected in the emulated executions.

Emulated breakdowns demonstrate that local disk executions will remain slower 
than Optane in both App Direct and Memory modes. Results show that both 
incrementation and write times will be generally be longer on local disk than
on Optane.

@@

Memory mode was found to result in increased computation time. When processing 
the 20~$\mu$m \bigbrain, Memory mode results indicate that more time was spent on
the incrementation tasks than its App Direct counterparts. Unlike App Direct mode,
which relies exclusively on DRAM for working memory, Memory mode relies on Optane
with a DRAM cache. Optane, while faster than other persistent storage devices, 
still lacks the bandwidth of DRAM. Should anonymous memory need to access Optane
for computation, it is not surprising that it would be slower than a DRAM-only
access. However, whereas Memory mode experienced increased computation during the
processing of the 20~$\mu$m \bigbrain, this was not always found to be the case
with the processing of the 40~$\mu$m \bigbrain. In fact, incrementation time was
largely similar between the two modes, with the notable exception of Optane in
Memory mode expending significantly less computation time than in App Direct when
processing the 40~$\mu$m \bigbrain with both 25 and 96 processes. Optane in 
Memory mode executing on local disk using 96 cpus, however, required significant
computation time as compared to App Direct. 
- Conclusion: memory mode should only be used when there's a requirement for additional memory
-App Direct mode results in increased I/O time for Optane
- conclusion: Optane might benefit from the DRAM cache
